Raft Distributed Consensus Algorithm over WebRTC (Web Real-Time Communication)

### 2015-09-16 research_class/paper.tex
Clarify sentence subject, add commas.
Add missing preposition.

\begin{enumerate}
\item The paper describes the Raft RPCs in terms of synchronous stream
    based request/response model where requests and responses are
    automatically correlated together by a lower level of the software
    stack. For example with HTTP 1.0 \cite{http:rfc1945} client
    requests are followed by a server response on any given TCP
    stream. Most remote procedure call mechanims also use
    a synchronous request/response model. %TODO/CITE
    WebRTC DataChannel connections are message based rather than
    request/response stream based. %TODO/CITE
    The original Raft definition of RPC request and response messages
    almost contain enough information to function correctly in an
    environment without builtin request/response correlation such as
    UDP or SCTP when used with reliable transport disabled. %TODO/CITE
    Raft.js includes a small modification to the response RPCs for
    requestVote and appendEntries to add a `sourceId' field that
    enables the protocol to function with message based transports.
\item The Raft paper is clear that each membership change must be
    delayed until all the previous membership change is committed
    (sequential) \cite[Section~4.1]{raft_thesis:ongaro14}. It is
    implied that the leader node should track all pending membership
    change requests and apply them one at a time.  However, in
    Raft.js, if a client requests a membership change while another
    change request is pending (uncommitted), the leader will reject
    the change request with a status of `PENDING\_CONFIG\_CHANGE'.
    This keeps the core Raft implementation simpler with the trade-off
    being that the client implementation of membership change requests
    is slightly more complex due to retry logic.
\end{enumerate}

@@

WebRTC is a collection of browser APIs \cite{webrtc:feb2015} and
network protocols \cite{draft-rtcweb-overview} that are currently
being standardized the W3C and IETF respectively. Collectively these
APIs and protocols enable real-time peer-to-peer video, audio and data
communication between browsers.

>>>>

\begin{enumerate}
\item The paper describes the Raft RPCs in terms of synchronous stream
    based request/response model where requests and responses are
    automatically correlated together by a lower level of the software
    stack. For example with HTTP 1.0 \cite{http:rfc1945} client
    requests are followed by a server response on any given TCP
    stream. Most remote procedure call mechanims also use
    a synchronous request/response model. %TODO/CITE
    WebRTC DataChannel connections are message based rather than
    request/response stream based. %TODO/CITE
    In the original Raft definition of RPC, request and response messages
    almost contain enough information to function correctly in an
    environment without builtin request/response correlation, such as
    UDP or SCTP when used with reliable transport disabled. %TODO/CITE
    Raft.js includes a small modification to the response RPCs for
    requestVote and appendEntries to add a `sourceId' field that
    enables the protocol to function with message based transports.
\item The Raft paper is clear that each membership change must be
    delayed until all the previous membership change is committed
    (sequential) \cite[Section~4.1]{raft_thesis:ongaro14}. It is
    implied that the leader node should track all pending membership
    change requests and apply them one at a time.  However, in
    Raft.js, if a client requests a membership change while another
    change request is pending (uncommitted), the leader will reject
    the change request with a status of `PENDING\_CONFIG\_CHANGE'.
    This keeps the core Raft implementation simpler with the trade-off
    being that the client implementation of membership change requests
    is slightly more complex due to retry logic.
\end{enumerate}

@@

WebRTC is a collection of browser APIs \cite{webrtc:feb2015} and
network protocols \cite{draft-rtcweb-overview} that are currently
being standardized by the W3C and IETF respectively. Collectively these
APIs and protocols enable real-time peer-to-peer video, audio and data
communication between browsers.
